The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-26 paper/sections/related.tex
figures
fixed typos and added an empty figure

%% Set the scene
Geometric modeling is a necessary precursor to physics-based animation, however differing geometric representations for modelling and simulation often require
time-consuming, complex geometry processing pipelines. 
For instance, the popular tetrahedral finite element approach for simulating solid elastodynamics~\cite{10.1145/2343483.2343501} requires robust algorithms for converting input surface geometry into 
a volumetric tetrahedral mesh. This is a difficult problem and while significant progress has been made,
even the most robust volumetric methods~\cite{Hu:2018:TMW:3197517.3201353} can be time consuming, fail to maintain correspondence between the input model and output simulation mesh,
and don't work directly on curved surface representations such as NURBS.

@@

\emph{Isogeometric Analysis}~\cite{10.1002/9780470749081.ch7} endeavors to perform simulation directly on the NURBS output from 
Computer-Aided Design (CAD) software. Initial attempts used NURBS surfaces to represent the mid-surface of thin objects~\cite{10.1145/176579.176580}.
Volumetric simulations relied on volumetric NURBS~\cite{10.1007/978-3-642-03596-8_2} but were limited to a narrow class of geometries.
Finite volume methods are applicable to more general geometries~\cite{HEINRICH20121645,10.1002/nme.2311} but require a volumetric mesh be generated.
Modern approaches are constructed around the extended finite element method which enriches the standard finite element basis with discontinuous basis functions
to enable improved boundary handling~\cite{https://doi.org/10.1002/nme.3120,10.1007/s00466-013-0854-7,https://doi.org/10.1002/nme.4852,SAFDARI2016373,10.1145/3355089.3356576}. 
These methods typically start with an easy-to-generate structured volumetric mesh (tetrahedral or hexahedral), ``cutting'' the NURBS geomtric model against
it to enable boundary handling (such a mesh is called a \emph{cutcell} mesh). 
Like volumetric meshing, this cutting operation can be difficult and our ideal method would avoid it. 
Some cutcell algorithms assume engineering/manufacturing quality input, which puts tight requirements on input models~\cite{10.1145/3355089.3356576}.
Finally these approaches require additional mechanisms to ensure that simulation results lie inside the shape space of the input model's primitives,
increasing complexity.

>>>>

%% Set the scene
Geometric modeling is a necessary precursor to physics-based animation, however differing geometric representations for modelling and simulation often requires
time-consuming, complex geometry processing pipelines. 
For instance, the popular tetrahedral finite element approach for simulating solid elastodynamics~\cite{10.1145/2343483.2343501} requires robust algorithms for converting input surface geometry into 
a volumetric tetrahedral mesh. This is a difficult problem and while significant progress has been made,
even the most robust volumetric methods~\cite{Hu:2018:TMW:3197517.3201353} can be time consuming, fail to maintain correspondence between the input model and output simulation mesh,
and don't work directly on curved surface representations such as NURBS.

@@

\emph{Isogeometric Analysis}~\cite{10.1002/9780470749081.ch7} endeavors to perform simulation directly on the NURBS output from 
Computer-Aided Design (CAD) software. Initial attempts used NURBS surfaces to represent the mid-surface of thin objects~\cite{10.1145/176579.176580}.
Volumetric simulations relied on volumetric NURBS~\cite{10.1007/978-3-642-03596-8_2} but were limited to a narrow class of geometries.
Finite volume methods are applicable to more general geometries~\cite{HEINRICH20121645,10.1002/nme.2311} but require a volumetric mesh to be generated.
Modern approaches are constructed around the extended finite element method which enriches the standard finite element basis with discontinuous basis functions
to enable improved boundary handling~\cite{https://doi.org/10.1002/nme.3120,10.1007/s00466-013-0854-7,https://doi.org/10.1002/nme.4852,SAFDARI2016373,10.1145/3355089.3356576}. 
These methods typically start with an easy-to-generate structured volumetric mesh (tetrahedral or hexahedral), ``cutting'' the NURBS geomtric model against
it to enable boundary handling (such a mesh is called a \emph{cutcell} mesh). 
Like volumetric meshing, this cutting operation can be difficult and our ideal method would avoid it. 
Some cutcell algorithms assume engineering/manufacturing quality input, which puts tight requirements on input models~\cite{10.1145/3355089.3356576}.
Finally these approaches require additional mechanisms to ensure that simulation results lie inside the shape space of the input model's primitives,
increasing complexity.
